An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-27 draft.tex
Updates bibliography on containers and evolutionary algorithms
Refs #2

Combining multiple algorithms, with different parameters, interacting with each
other at the same time, can benefit from the strengths of each. For instance, a
genetic algorithm could find a promising global solution that is not optimal
while another algorithm, more suitable for a local search, finds the global
optimum. This approach has been followed extensively in recent years, with
success. % References - JJ
Moreover, there is a need for frameworks, architecture, and
implementation models that can allow researchers the development of new
parallel, asynchronous, heterogeneous, and parameter-free algorithms in a scalable way.

\section{State of the Art} 
\label{soa}
% a lot of this has been done in the previous method... Maybe there's
% not that much to do - JJ
Hadoop 
    Comparison \cite{ferrucci2018using}
    Hadoop\cite{fazenda2012} 
    FlexGP \cite{FlexGP}, 
    elephant56 \cite{salza2016elephant56},

Pool
    SofEA \cite{merelo2012sofea,sofea:cec2012} , 
    EvoSpace \cite{garcia2015evospace},
Volunteer
    evospace-js \cite{garcia2017evospace}
Queue
    Containers \cite{valenzuela2015implementing} \cite{salza2016approach} 
    Seamless local and Cloud \cite{leclerc2016seamless}
    Serverless KafKEO \cite{guervos2018introducing}, 
    Docker Orchestation \cite{dziurzanski2020scalable,zhao2019cloud}
PSO 
    PSO AWS \cite{li2015parallel}

>>>>

Combining multiple algorithms, with different parameters, interacting with each
other at the same time, can benefit from the strengths of each. For instance, a
genetic algorithm could find a promising global solution that is not optimal
while another algorithm, more suitable for a local search, finds the global
optimum. This approach has been followed extensively in recent years with
success. % References - JJ
Moreover, there is a need for frameworks, architecture, and
implementation models that can allow researchers the development of new
parallel, asynchronous, heterogeneous, and parameter-free algorithms in a scalable way.

\section{State of the Art} 
\label{soa}
% a lot of this has been done in the previous method... Maybe there's
% not that much to do - JJ
% Hadoop 
%     Comparison \cite{ferrucci2018using}
%     Hadoop\cite{fazenda2012} 
%     FlexGP \cite{FlexGP}, 
%     elephant56 \cite{salza2016elephant56},

% Pool
%     SofEA \cite{merelo2012sofea,sofea:cec2012} , 
%     EvoSpace \cite{garcia2015evospace},
% Volunteer
%     evospace-js \cite{garcia2017evospace}
% Queue
%     Containers \cite{valenzuela2015implementing} \cite{salza2016approach} 
%     Seamless local and Cloud \cite{leclerc2016seamless}
%     Serverless KafKEO \cite{guervos2018introducing}, 
%     Docker Orchestation \cite{dziurzanski2020scalable,zhao2019cloud}
% PSO 
% PSO AWS \cite{li2015parallel}
